---
params:
  titleName: NULL
  user_inputs: NULL
  omicsData: NULL
  tables: NULL
  plots: NULL
  
title: "`r params$titleName`"
date: "`r format(Sys.time(), '%B %d, %Y')`"
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(shiny)
library(pmartR)
library(knitr)
library(stringi)
fixcomma <- function(x) {
  if (str_count(x, ",") > 1) {
    stri_replace_last(x, ", and ", fixed = ", ")
  } else if (str_count(x, ",") > 0) {
    stri_replace_last(x, " and ", fixed = ", ")
  } else {
    x
  }
}
condense <- function(x) {
  wordcount <- str_count(x, ", ")
  wordcount <- wordcount + 1
  if (wordcount < 6)
    return(fixcomma(x))
  elements <- str_split(x, ", ")[[1]]
  paste0(elements[1], ", ", elements[2], ", ", elements[3], ", and ", wordcount - 3, " more")
}
```

## Initial Data Upload

```{r Upload}
text <- "A "
text <- paste0(text, params$user_inputs$upload$data_type)
text <- paste0(text, " abundance data file sourced from ")
text <- paste0(text, params$user_inputs$upload$edata_source) 

if (params$user_inputs$upload$edata_source == "Uploaded Data") {
  text <- paste0(text, " called ", params$user_inputs$upload$edata_filename)
}

text <- paste0(text, " was uploaded to the SLOPE application. This file contains ")
text <- paste0(text, length(params$omicsData$obj$e_data) - 1)
text <- paste0(text, " samples and ")
text <- paste0(text, length(unique(params$omicsData$obj$e_data[[params$user_inputs$upload$edata_idcol]])))
text <- paste0(text, " biomolecules designated by the **")
text <- paste0(text, params$user_inputs$upload$edata_idcol)
text <- paste0(text, "** column. The data were imported as ")
text <- paste0(text, switch(params$user_inputs$upload$edata_datascale, 
                            abundance = "raw intensity",
                            log2 = "log base 2 scaled",
                            log10 = "log base 10 scaled",
                            log = "natural log scaled"))
text <- paste0(text, " ")
text <- paste0(text, if (params$user_inputs$upload$edata_norm == "No") "unnormalized" else "normalized")
text <- paste0(text, " data, with \"")
text <- paste0(text, params$user_inputs$upload$edata_nasymbol)
text <- paste0(text, "\" denoting missing values.")

if (!is.null(params$user_inputs$upload$fdata_source) && params$user_inputs$upload$fdata_source != "None") {
  text <- paste0(text, "\\\n")
  text <- paste0(text, "An associated sample information file sourced from ")
  text <- paste0(text, params$user_inputs$upload$fdata_source)
  
  if (params$user_inputs$upload$fdata_source == "Uploaded Data") {
    text <- paste0(text, " called ", params$user_inputs$upload$fdata_filename)
  }
  
  text <- paste0(text, " was also uploaded to the SLOPE application. The sample identifier column was designated as **")
  text <- paste0(text, params$user_inputs$upload$fdata_idcol)
  text <- paste0(text, "**. The file contains ")
  text <- paste0(text, length(params$omicsData$obj$f_data))
  text <- paste0(text, " columns of sample information.")
}

if (!is.null(params$user_inputs$upload$emeta_source) && params$user_inputs$upload$emeta_source != "None") {
  text <- paste0(text, "\\\n")
  text <- paste0(text, "An associated biomolecule information file sourced from ")
  text <- paste0(text, params$user_inputs$upload$emeta_source)
  
  if (params$user_inputs$upload$emeta_source == "Uploaded Data") {
    text <- paste0(text, " called ", params$user_inputs$upload$emeta_filename)
  }
  
  text <- paste0(text, " was also uploaded to the SLOPE application. The molecule identifier column was designated as **")
  text <- paste0(text, params$user_inputs$upload$emeta_idcol)
  text <- paste0(text, "**. The file contains ")
  text <- paste0(text, length(params$omicsData$obj$e_meta))
  text <- paste0(text, " columns of biomolecule information.")
}
```

`r text`
\

Below is a truncated portion containing the first 3 columns and 10 rows of each of the files. The full files are available in the zip archive.
\


Abundance Data: \

```{r Upload abundance data}
trunc <- params$tables$table$Upload__e_data
trunc <- trunc[,1:min(dim(trunc)[2],3)]
trunc <- trunc[1:min(dim(trunc)[1], 10),]
trunc <- data.frame(lapply(trunc, \(x) sapply(x, \(x2) if (is.na(x2)) NA else if (nchar(as.character(x2)) > 18) paste0(strtrim(as.character(x2), 18), "...") else as.character(x2))))
kable(trunc)
```
\


Sample Information: \

```{r Upload sample info}
trunc <- params$tables$table$Upload__f_data
trunc <- trunc[,1:min(dim(trunc)[2],3)]
trunc <- trunc[1:min(dim(trunc)[1], 10),]
trunc <- data.frame(lapply(trunc, \(x) sapply(x, \(x2) if (is.na(x2)) NA else if (nchar(as.character(x2)) > 18) paste0(strtrim(as.character(x2), 18), "...") else as.character(x2))))
kable(trunc)
```
\

`r if (!is.null(params$tables$table$Upload__e_meta)) "\nBiomolecule Information: \\newline"`
```{r Upload biomolecule info}
if (!is.null(params$tables$table$Upload__e_meta)) {
  trunc <- params$tables$table$Upload__e_meta
  trunc <- trunc[,1:min(dim(trunc)[2],3)]
  trunc <- trunc[1:min(dim(trunc)[1], 10),]
  trunc <- data.frame(lapply(trunc, \(x) sapply(x, \(x2) if (is.na(x2)) NA else if (nchar(as.character(x2)) > 18) paste0(strtrim(as.character(x2), 18), "...") else as.character(x2))))
  kable(trunc)
}
```
`r if (!is.null(params$tables$table$Upload__e_meta)) "\\"`

Abundance Data Boxplots: \

```{r Upload boxplot}
if (is.null(params$plots$table$Upload__boxplot))
{
  "Plot was not generated in the SLOPE session."
} else {
  params$plots$table$Upload__boxplot
}
```
\

\newpage

## Quality Control

```{r QC}
text <- ""

if (inherits(params$omicsData$obj, "nmrData") && !is.null(params$user_inputs$refnorm_applied) && params$user_inputs$refnorm_applied == "Yes") {
  text <- paste0(text, "The data was referenced normalized using the ")
  text <- paste0(text, params$user_inputs$refnorm_identifier, " identifier from ")
  text <- paste0(text, params$user_inputs$refnorm_source, ".")
}

if (inherits(params$omicsData$obj, "isobaricpepData")) {
  text <- paste0(text, "The data was referenced normalized using ")
  text <- paste0(text, params$user_inputs$qc$ref_group, " as the group, and ")
  text <- paste0(text, params$user_inputs$qc$ref_notation, " values in the ")
  text <- paste0(text, params$user_inputs$qc$ref_col, " column as the reference sample identifiers.\\\n")
}

if (params$user_inputs$qc$single_obs_removed == "Yes") {
  text <- paste0(text, params$user_inputs$filters$single_molfilt, " biomolecules for which only a single observation was detected were discarded. ")
}
```

`r text`
\

Single Observation Biomolecules: \

```{r Single Obs}
if (is.null(params$plots$table$QC__single_obs))
{
  "Plot was not generated in the SLOPE session."
} else {
  params$plots$table$QC__single_obs
}
```
\

\newpage

```{r QC RMD}
text <- ""
if (params$user_inputs$qc$outliers_removed != "None") {
  text <- paste0(text, "Samples ", condense(params$user_inputs$qc$outliers_removed), " were marked as outliers and removed. ")
}
```

`r text`

`r if(!inherits(omicsData$objQC, "seqData")) "Robust Mahalanobis Distance Outlier Detection: \\" else ""`

```{r RMD outliers}
if(!inherits(omicsData$objQC, "seqData")) {
  if (is.null(
    params$plots$table$QC__rmd_overall
  ))
  {
    "Plot was not generated in the SLOPE session."
  } else {
    params$plots$table$QC__rmd_overall
  }
}
```

\newpage

```{r QC Missingness}
text <- paste0(text, "Samples with more than ", params$user_inputs$qc$min_pct_sample, "% missingness were removed. Missing data was chosen to be ")

if (params$user_inputs$qc$missingdata_kept == "Yes") {
  text <- paste0(text, "kept.")
} else {
  if (params$user_inputs$qc$handle_impute != "None") {
    text <- paste0(text, "estimated for biomolecules with ", params$user_inputs$qc$handle_impute, "% missingness")
  }
  
  if (params$user_inputs$qc$handle_convert != "None") {
    if (params$user_inputs$qc$handle_impute != "None" && params$user_inputs$qc$handle_remove == "None") {
      text <- paste0(text, " and ")
    } else if (params$user_inputs$qc$handle_impute != "None" && params$user_inputs$qc$handle_remove != "None") {
      text <- paste0(text, ", ")
    }
    
    text <- paste0(text, "converted to presence/absence for biomolecules with ", params$user_inputs$qc$handle_convert, "% missingness")
  }
  
  if (params$user_inputs$qc$handle_remove != "None") {
    if (params$user_inputs$qc$handle_impute != "None" && params$user_inputs$qc$handle_convert == "None") {
      text <- paste0(text, " and ")
    } else if (params$user_inputs$qc$handle_impute != "None" && params$user_inputs$qc$handle_convert != "None") {
      text <- paste0(text, ", and ")
    }
    
    text <- paste0(text, "removed for biomolecules with ", params$user_inputs$qc$handle_remove, "% missingness. ")
  }
}
```

Sample Missingness: \

```{r Sample Missingness}
if (is.null(
  params$plots$table$QC__missing_samples
  ))
{
  "Plot was not generated in the SLOPE session."
} else {
  params$plots$table$QC__missing_samples
}
```

`r if (params$user_inputs$qc$missingdata_kept != "Yes") "Biomolecule Missingness: \\"`

```{r QC Missingness Plot}
if (params$user_inputs$qc$missingdata_kept != "Yes") {
  if (is.null(
    params$plots$table$QC__missing_features
    ))
  {
    "Plot was not generated in the SLOPE session."
  } else {
    suppressWarnings(
      params$plots$table$QC__missing_features
    )
  }
}
```
\

\newpage

## Model Set-Up

```{r Model Set-Up}
text <- "Columns "
text <- paste0(text, fixcomma(params$user_inputs$msu$tracked_cols))
text <- paste0(text, " of the sample information were selected to be tracked in the application, of which ")
text <- paste0(text, fixcomma(params$user_inputs$msu$categorical_cols))
text <- paste0(text, " were marked as categorical. For model selection, ")
text <- paste0(text, str_to_lower(params$user_inputs$msu$model_type))
text <- paste0(text, " models were explored, with ")
text <- paste0(text, str_to_lower(params$user_inputs$msu$model_priority))
text <- paste0(text, " being the priority.")
if (str_to_lower(params$user_inputs$msu$model_type) == "supervised")
{
  text <- paste0(text, " The **", params$user_inputs$msu$response_var, "** column of the sample information was selected to be the response variable.")
}
text <- paste0(text, " The chosen model was **")
text <- paste0(text, params$user_inputs$msu$model_selected)
text <- paste0(text, "** and was the #")
text <- paste0(text, params$user_inputs$msu$model_selected_index)
text <- paste0(text, " model recommended by Expert Mentor.")
```

`r text`
\

Expert Mentor Summary:
```{r Expert Mentor Summary}
kable(params$tables$table$MSU__expert_mentor_summary[,1:2])
```
\

\newpage

## Pre-processing

### Transform

```{r PP Transform}
text <- "The data was transformed to "
text <- paste0(text, switch(params$user_inputs$pp$transform, 
                            abundance = "raw intensity",
                            log2 = "log base 2",
                            log10 = "log base 10",
                            log = "natural log"))
text <- paste0(text, " scale. \\\n\\\n")
```

`r text`

Transformed Boxplots: \

```{r PP Transform Plot}
if (is.null(
  params$plots$table$PP__transform
  ))
{
  "Plot was not generated in the SLOPE session."
} else {
  params$plots$table$PP__transform
}
```

\newpage

### Filters

```{r PP Molfilt}
text <- ""
if (!is.null(params$user_inputs$pp$molfilt) && params$user_inputs$pp$molfilt)  {
  text <- paste0(text, "A molecule filter was applied with a minimum threshold of ")
  text <- paste0(text, params$user_inputs$pp$molfilt_min_num)
  text <- paste0(text, " observations. The filter removed ")
  text <- paste0(text, params$user_inputs$filters$molfilt, " biomolecule", ifelse(params$user_inputs$filters$molfilt != 1, "s", ""), ". \\\n")
}
```

`r text`

`r if (!is.null(params$plots$table$PP__filters__molfilt)) "Molecule Filter: \\"`
```{r Molecule Filter}
if (!is.null(params$plots$table$PP__filters__molfilt)) {
  params$plots$table$PP__filters__molfilt
}
```
`r if (!is.null(params$plots$table$PP__filters__molfilt)) "\\"`

\newpage

```{r PP imputeFilt}
text <- ""
if (!is.null(params$user_inputs$pp$imputefilt) && params$user_inputs$pp$imputefilt) {
  text <- paste0(text, "An imputation filter was applied which ")
  if (params$user_inputs$pp$handle_impute != "None") {
    text <- paste0(text, "estimated missing data for biomolecules with ", params$user_inputs$pp$handle_impute, "% missingness")
  }
  
  if (params$user_inputs$pp$handle_convert != "None") {
    if (params$user_inputs$pp$handle_impute != "None" && params$user_inputs$pp$handle_remove == "None") {
      text <- paste0(text, " and ")
    } else if (params$user_inputs$pp$handle_impute != "None" && params$user_inputs$pp$handle_remove != "None") {
      text <- paste0(text, ", ")
    }
    
    text <- paste0(text, "converted biomolecules with ", params$user_inputs$pp$handle_convert, "% missingness to presence/absence")
  }
  
  if (params$user_inputs$pp$handle_remove != "None") {
    if (params$user_inputs$pp$handle_impute != "None" && params$user_inputs$pp$handle_convert == "None") {
      text <- paste0(text, " and ")
    } else if (params$user_inputs$pp$handle_impute != "None" && params$user_inputs$pp$handle_convert != "None") {
      text <- paste0(text, ", and ")
    }
    
    text <- paste0(text, "removed biomolecules with ", params$user_inputs$pp$handle_remove, "% missingness")
  }
  
  text <- paste0(text, ". \\\n")
}
```

`r text`

`r if (!is.null(params$plots$table$PP__filters__imputefilt)) "Imputation Filter: \\"`

```{r Imputation Filter}
if (!is.null(params$plots$table$PP__filters__imputefilt)) {
  params$plots$table$PP__filters__imputefilt
}
```
`r if (!is.null(params$plots$table$PP__filters__imputefilt)) "\\"`

\newpage

```{r PP CVFilt}
text <- ""
if (!is.null(params$user_inputs$pp$cvfilt) && params$user_inputs$pp$cvfilt) {
  text <- paste0(text, "A coefficient of variation filter was applied with a CV threshold of ")
  text <- paste0(text, params$user_inputs$pp$cvfilt_threshold)
  if (params$user_inputs$pp$cvfilt_use_groups) {
    text <- paste0(text, " using groups")
  }
  text <- paste0(text, ". The filter removed ")
  text <- paste0(text, params$user_inputs$filters$cvfilt, " biomolecule", ifelse(params$user_inputs$filters$cvfilt != 1, "s", ""), ". \\\n")
}
```

`r text`

`r if (!is.null(params$plots$table$PP__filters__cvfilt)) "CV Filter: \\"`

```{r CV Filter}
if (!is.null(params$plots$table$PP__filters__cvfilt)) {
  params$plots$table$PP__filters__cvfilt
}
```
`r if (!is.null(params$plots$table$PP__filters__cvfilt)) "\\"`

\newpage

```{r PP TCFilt}
text <- ""
if (!is.null(params$user_inputs$pp$tcfilt) && params$user_inputs$pp$tcfilt) {
  text <- paste0(text, "A total count filter was applied with a minimum count of ")
  text <- paste0(text, params$user_inputs$pp$tcfilt_min_count)
  text <- paste0(text, ". The filter removed ")
  text <- paste0(text, params$user_inputs$filters$tcfilt, " biomolecule", ifelse(params$user_inputs$filters$tcfilt != 1, "s", ""), ". \\\n")
}
```

`r text`

`r if (!is.null(params$plots$table$PP__filters__totalCountFilt)) "Total Count Filter: \\"`

```{r TC Filter}
if (!is.null(params$plots$table$PP__filters__totalCountFilt)) {
  params$plots$table$PP__filters__totalCountFilt
}
```
`r if (!is.null(params$plots$table$PP__filters__totalCountFilt)) "\\"`

\newpage

```{r PP Libfilt}
text <- ""
if (!is.null(params$user_inputs$pp$libfilt) && params$user_inputs$pp$libfilt) {
  text <- paste0(text, "A library size filter was applied with a minimum library size of ")
  text <- paste0(text, params$user_inputs$pp$libfilt_min_libsize)
  text <- paste0(text, ". The filter removed ")
  text <- paste0(text, params$user_inputs$filters$libfilt, " sample", ifelse(params$user_inputs$filters$libfilt != 1, "s", ""), ". \\\n")
}
```

`r text`

`r if (!is.null(params$plots$table$PP__filters__Libfilt)) "Library Size Filter: \\"`

```{r Lib Filter}
if (!is.null(params$plots$table$PP__filters__Libfilt)) {
  params$plots$table$PP__filters__Libfilt
}
```
`r if (!is.null(params$plots$table$PP__filters__Libfilt)) "\\"`

\newpage

```{r PP Customfilt}
text <- ""
if (params$user_inputs$pp$customfilt) {
  text <- paste0(text, "A custom filter was applied which ")
  if (params$user_inputs$pp$customfilt_handling == "keep") {
    text <- paste0(text, "kept the following biomolecules: ")
  } else {
    text <- paste0(text, "removed the following biomolecules: ")
  }
  text <- paste0(text, condense(paste(params$user_inputs$pp$customfilt_regex, collapse = ", ")))
  text <- paste0(text, ". The filter removed ")
  text <- paste0(text, params$user_inputs$filters$customfilt, " biomolecule", ifelse(params$user_inputs$filters$customfilt != 1, "s", ""), ". \\\n")
}
```

`r text`

\newpage

### Normalization

```{r PP Normalization}
text <- ""
if (params$user_inputs$pp$norm_method != "No Normalization") {
  text <- paste0(text, "\\\nThe data was then normalized using ")
  text <- paste0(text, params$user_inputs$pp$norm_method)
  text <- paste0(text, ". ")
  
  if (params$user_inputs$pp$norm_method == "Global Normalization") {
    text <- paste0(text, "The ")
    text <- paste0(text, params$user_inputs$pp$norm_fn)
    text <- paste0(text, " normalization function was used and the ")
    text <- paste0(text, params$user_inputs$pp$norm_subset_fn)
    text <- paste0(text, " subset function was used. ")
    
    if (params$user_inputs$pp$norm_subset_fn == "Percentage present and rank invariant (ppp+rip)") {
      text <- paste0(text, "The percentage present threshold used was ")
      text <- paste0(text, params$user_inputs$pp$norm_ppp)
      text <- paste0(text, " and the rank invariant p-value threshold used was ")
      text <- paste0(text, params$user_inputs$pp$norm_rip)
      text <- paste0(text, ". ")
    }
  }
} else {
  text <- "Normalization was not applied."
}
```

`r text`

`r if(params$user_inputs$pp$norm_method != "No Normalization") "Normalized Data Boxplots: \\" else ""`

```{r Normalized Boxplots}
if (params$user_inputs$pp$norm_method != "No Normalization") {
  if (is.null(
  params$plots$table$PP__normalization__post
  ))
{
  "Plot was not generated in the SLOPE session."
} else {
  params$plots$table$PP__normalization__post
}
}
```

```{r PP Rollup}
text <- ""

if (!is.null(params$user_inputs$pp$rollup_method)) {
  text <- paste0(text, "\\newpage\n\n### Rollup\n\\\nThe data was then rolled up to the protein level using the ")
  text <- paste0(text, params$user_inputs$pp$rollup_method, " rollup method, centered by ")
  text <- paste0(text, params$user_inputs$pp$rollup_combine_fn)
  text <- paste0(text, ". ")
}
```

`r text`

`r if (!is.null(params$plots$table$PP__rollup)) "Post-rollup Boxplots: \\"`

```{r Rollup Boxplots}
if (!is.null(params$plots$table$PP__rollup)) {
  params$plots$table$PP__rollup
}
```
`r if (!is.null(params$plots$table$PP__rollup)) "\\"`

\newpage

## Run Model

```{r Run Model}

text <- ""
if (str_to_lower(params$user_inputs$msu$model_type) == "supervised") {
text <- paste0("A ", params$user_inputs$msu$model_selected, " model predicting the ")
text <- paste0(text, params$user_inputs$msu$response_var, " value was created with the purpose of running on ")
text <- paste0(text, switch(params$user_inputs$rm$model_scope,
                            "Current Data" = "the uploaded dataset only",
                            "the uploaded dataset and future datasets"), ". ")
text <- paste0(text, "Hyperparameter values were sourced from ")
if (params$user_inputs$rm$hyperparam_source == "Default")
  text <- paste0(text, "default values used for training ", params$user_inputs$msu$model_selected, " models")
else {
  text <- paste0(text, str_to_lower(params$user_inputs$rm$hyperparam_source), " values")
}
text <- paste0(text, ". \\\n")
  text <- paste0(text, "The model was assessed using ", 
                 switch(
                        params$user_inputs$rm$subset_method,
                        "K-fold" = paste0(params$user_inputs$rm$nfolds, "-fold"),
                        "leave-one-out"
                 ),
          " cross-validation. ")
  if (!is.null(params$plots$table$RM__model_eval__reduced__roc_curve))
  {
    text <- paste0(text, 
          ifelse(params$user_inputs$rm$vi_choose == "value", "Features with an importance value above ", "The top "),
          params$user_inputs$rm$vi_value,
          " ",
          switch(params$user_inputs$rm$vi_choose,
                  value = "",
                  count = " features",
                  percent = " percent of features"),
          " were used to create a reduced model.")
  }
} else {
  text <- paste0("A ", params$user_inputs$msu$model_selected, " model was created ")
  text <- paste0(text, "using hyperparameter values were sourced from ")
  if (params$user_inputs$rm$hyperparam_source == "Default")
    text <- paste0(text, "default values used for training ", params$user_inputs$msu$model_selected, " models")
  else {
    text <- paste0(text, str_to_lower(params$user_inputs$rm$hyperparam_source), " values")
  }
  text <- paste0(text, ". \\\n")
}
```

`r text`
\

`r if (!is.null(params$plots$table$RM__rec_folds)) "Training Structure Recommendation: \\"`

```{r Fold optimization}
if (!is.null(params$plots$table$RM__rec_folds)) {
  params$plots$table$RM__rec_folds
}
```
`r if (!is.null(params$plots$table$RM__rec_folds)) "\\"`

```{r}

text <- ""
if (params$user_inputs$msu$model_type == "Supervised") {
  text <- "Training Structure: \\"
}
```

`r text`

```{r Training Structure}
if (params$user_inputs$msu$model_type == "Supervised") {
  params$plots$table$RM__training_structure
}
```
\

Model Hyperparameters: \

```{r Hyperparams}
kable(params$user_inputs$rm$hyperparams)
```
\

```{r}
if (params$user_inputs$msu$model_type == "Supervised") {
  text <- "Model ROC Curve: \\"
} else {
  text <- "Model Result: \\"
}
```

`r text`

```{r Accuracy}

text <- ""
if (params$user_inputs$msu$model_type == "Supervised") {
  if (is.null(params$plots$table$RM__model_eval__reduced__roc_curve)) {
    params$plots$table$RM__model_eval__full__roc_curve
  } else {
    params$plots$table$RM__model_eval__reduced__roc_curve
  }
} else {
  params$plots$table[[length(params$plots$table)]]
}
```
\

```{r}
# Reduced
```

```{r}
text <- ""
if (params$user_inputs$msu$model_type == "Supervised") {
  text <- "ROC Details: \\"
}
```

`r text`

```{r}
if (params$user_inputs$msu$model_type == "Supervised") {
  pred_df <- attr(params$omicsData$objRM, "prediction_train")
  
  if (!is.null(omicsData$objRM_reduced)) {
    pred_df <- attr(params$omicsData$objRM_reduced, "prediction_train")
  }
  
  if (length(unique(pred_df$response)) == 2) {
    pos_class <- names(pred_df)[3]
    p <- yardstick::roc_curve(pred_df, response, dplyr::all_of(pos_class))  
    p[".level"] <- gsub(".pred_", "", pos_class)
  } else {
    pos_class <- names(pred_df)[3:(2+length(unique(pred_df$response)))]
    p <- yardstick::roc_curve(pred_df, response, dplyr::all_of(pos_class))   
  }
  
  auc_by_level <- p %>%
    dplyr::group_by(.level) %>%
    dplyr::mutate(spc_diff = specificity - dplyr::lag(specificity),
                  sens_avg = (sensitivity + dplyr::lag(sensitivity))/2) %>%
    dplyr::summarise(sum(spc_diff*sens_avg, na.rm=T))
  
  names(auc_by_level)[1] <- "Group"
  names(auc_by_level)[2] <- "AUC of ROC"
  
  auc_by_level
  
  kable(auc_by_level)
}
```
